\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-02-28 papers/itsc_2012/draft2.tex
lazy atomic queue-checking; in-place often suffices. considerable speedup.
measuring number of moves/second... very comforting number

@@

@@

All traversables (edges and the straight line-approximation of turns) maintain
an ordered queue of occupying agents. Agents stepping forward in time happens
atomically, so collision checking occurs after all agents have moved for some
tick. This is done because otherwise false positives could occur when an agent
steps before the agent in front of it, and ordering agents for updates is
difficult near the crossings between edges. \commentd{Do I need to explain why
it is difficult, or should I just stop after ``in front of it''?} A collision is
defined as the reversal of order of agents before and after a step.

@@

>>>>

\commentd{last sentence above... we're not not doing that yet, and we dont
  discuss it further here.}

@@

\commentd{space continuous? get terminology right}

@@

All traversables (edges and the straight line-approximation of turns) maintain
an ordered queue of occupying agents. Agents stepping forward in time happens
atomically, so collision checking occurs after all agents have moved for some
tick. This is done because otherwise false positives could occur when an agent
steps before the agent in front of it, and ordering agents for updates is
difficult near the crossings between edges. \commentd{Do I need to explain why
it is difficult, or should I just stop after ``in front of it''?} A collision is
defined as the reversal of order of agents before and after a step.
\commentd{lazy queue checking for speedup. mention briefly?}

@@

\commentd{http://sumo.sourceforge.net/pdf/mieec1.pdf gives their measure as
  agent updates / second. This is indep of dt and num of agents, assuming
  nothing grows nonlinearly with more agents. our initial result on my box is
  about 150,000 moves / second. so with 500 agents, runs 30x faster than
  reality. with 5,000, runs about 3x faster. with 50,000 (yes, this works!),
  runs at 1/3 the speed of reality (it takes 1 real second to simulate 0.3
  seconds)}
